MR10..

Hi.  Welcome.  OK, you know you need to be here the same time on
Wednesday.  Also, sit at the same computer on Wednesday.

This is an experiment in memory.  We are going to present you items
and each item is going to be paired with a two-digit number.  The top
row shows four shapes.  Each shape is paired with a two-digit number.
Your job is to learn the number for each shape.  Hit <enter> now.
Here is a shape.  You don't know the two-digit number, so you might
guess 99.  Use the number rows (not the number pad) to enter '99' now.
Because this is a guess, we are destined to be wrong.  When you are
wrong, the computer shows you the correct answer.  See it?  Study it.
The next time this shape comes up, enter that two digit number.  Ok?
Once you are done studying this shape-number pair, hit any key and a
new shape will come up.  There are only four shapes to learn, and you
need to get 8 correct in a row.  We are measuring how long it takes
you to learn the four items.  It takes about two minutes to learn a set.
Any questions?

OK.  Now when you are done learning those four items, the computer
will display a sign that says ``New Set''.  Take a break for a minute
and clear your head.  You are now going to learn four items in a
different set.  These items will have different numbers associated
with them, and you will learn the new numbers.  There are a total of
five sets.  Any questions?

Ok. Before we contunue I want to review the five sets.  The first set
is shapes.  After that, everybody has a different order of sets.  One
of the sets will be the four English letters shown on the sheet.
Another will be characters from a different alphabet.  A third set
will be checker-board patters.  Each of these patterns has a different
contrast.  The first one is of low contrast, the blacks aren't black
and the whites arent too white.  The last one is of high contrast, the
black is really black and the white is really white.  Each of the four
checkerboards will be assigned a different two-digit number.  The
remaining set is four different line-lengths.

Any questions.

When your done, come see me in 205 at the end of the hall.

 

